\section{Hardware Platform} \label{sec:platform}
Before things like the architecture or the User Interface of our application can be designed, we have to decide on a platform to implement our application on. We found that the majority of the existing Smart Home solutions we investigated have a mobile application, but that is not necessarily the best choice. Examining the positives and negatives of the different potential platforms will help us find the right one for our application. The main requirements for the platform is that it must support Internet technology and must be easily accessible in the home.

\subsection{Phone}
The first possibility is to make a smartphone application. Creating the application for both Android, iOS, and Windows Phone will allow almost every smartphone user to use the application. Besides being accessible on a smartphone, it will also be available on tablets, which in 2015 could be found in every second Danish home~\citep{dst-elektronik}. The biggest benefit is therefore that the system is easily accessible to the user. 

\subsection{Computer}
The second alternative is to make the application for computers. This solution will need platform specific development for both MAC OS, Linux, and Windows. Making the application available for computers will also hit the biggest audience. 85\% of Danish homes contains at least one laptop, making it the most popular device on which such an application can be used~\citep{dst-elektronik}.

\subsection{Multi-Platform}
The third possibility is to develop a web application. A web application runs in the browser, and can therefore be accessed through either a smart phone, tablet, or computer, resulting in only having to make the web application for one platform. Since the web application is running on a remote server, the user does not have to download and update the application. This also removes the possibility for the users to have version conflicts. This solution will require both a server and a client running on all devices. 

\subsection{Platform Choice}
Choose platform, internet

